Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-06 WSSSPE1_report/WSSSPE1_summary_report.tex
Added some introduction to backward compatibility

>>>>

Software is developed for many different purposes, and the requirements can
vary significantly depending on the intended audience. Most end-users make use
of either a graphical user interface of some kind, or a command line that may
offer input and output formats for running the code and analyzing its output(s).
When discussing backward compatibility it is these various interfaces that are
discussed. For software that builds on other software frameworks it is the
API (application programming interface) that is most important, and this can
encompass issues such as the source and binary interfaces to the software
libraries developed---with each potentially having a high maintenance cost if
they are to remain compatible over many years. When using command line programs
it is generally the command line switches as well as the input/output formats
that could incur significant costs if they are changed.
